---
title: "Exogenous variables GARCH"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

Earlier contributions in the literature (Kalev et al., 2004;
Bomfim, 2001, inter alia) https://www.sciencedirect.com/science/article/pii/S0378426603001262 suggest the use of GARCH (Engle, 1982;
Bollerslev, 1986) http://www.jstor.org/stable/1912773?casa_token=u70jYdYfQiYAAAAA:SW-edrtQyiFR4KifaoqS-ArpjLued8DA3n4JhtqN8HWgbyTq_9jkKpyKkKVy2BHLVo4ZZkyNbdwn5vECozBBh5Jztg1N6q2ALW_c8KwYYAEp67IX&seq=1#page_scan_tab_contents models for approximating historical volatility.

Although this approach can be expected to be less accurate than
the realized volatility used previously, since the latter utilizes
much more data, it has the advantage of being able to model the
conditional mean and variance at the same time in a straightforward
manner. Moreover, a wealth of empirical evidence exists on
the application of GARCH models in finance. We model conditional
volatility through the use of a GARCH(1,1) market model that includes
information demand and supply variables in the conditional
variance specification: 

\begin{align}
    r_t = \mu + \lambda\nu_t + \epsilon_t,\hspace{0.5pt}\epsilon_t | \Omega_{t-1} \approx N(o,\sigma^2_t)\\
    \sigma^2_t = w + \alpha\epsilon^2_{t-1} + \beta\sigma^2_{t-1} + \gamma\pi_t + \delta\phi_t
\end{align}

where $r_t$ is the stock return at interval $t$, $\mu$ is a constant, $\epsilon_t$ are the serially uncorrelated errors of stock returns with mean zero, $\Omega_{t-1}$
denotes the information set, $\sigma^2_t$
is the conditional variance of $\epsilon_t$,
whereas $\nu_t$ is the market return, $\pi_t$ is idiosyncratic information demandand  $\phi_t$ is market related information demand .


The first thing is to import the data previously generated. 

```{r}
library(rugarch)
library(tidyverse)
library(lubridate)
# Format numbers
options(scipen = 50)
df <- read_csv('/data/GARCH_model.csv')
head(df)

```

Now estimate the model for all time series

```{r}
id_ticker = unique(df$Ticker)

exo_levels = c('SPY')
exo_vol = c('SVI','market_info')
  GARCH_model <- function(x){
                      # ''' For ticker x estimate the GARCH model'''
                      
                      # x =tail(x,200)
                      # Specify model
                      spec1 =ugarchspec(variance.model=list(model="sGARCH",
                                  external.regressors =  as.matrix(subset(x, select = exo_vol))),
                      mean.model=list(armaOrder=c(0,0), include.mean=TRUE ))
                      
                      # Fit model
                      fit = ugarchfit(spec = spec1, x$ret, solver = 'hybrid')
                      # Pvalues
                      Pvalues = fit@fit$robust.matcoef[,4]
                      names(Pvalues) =lapply(names(fit@fit$coef), function(x){return(paste0('p_',x))})
                      # Coeficients
                      Coeficients = fit@fit$robust.matcoef[,1]
                      
                      ret = c(Pvalues, Coeficients)
                      return(ret)
}

garch_results = df %>% 
  split(.$Ticker) %>% 
  map(GARCH_model)

garch_results = t(as.data.frame(garch_results))
garch_results
```

Financial theory suggests that an asset with a higher expected risk would pay a higher
return on average.The relationship between investors’ expected return and risk was presented in
an ARCH framework by Engle et al. (1987). They introduced the ARCH in mean, or
ARCH-M, model where the conditional mean is an explicit function of the conditional
variance of the process. \

To overcome some weaknesses of the GARCH model in handling financial time
series, Nelson (1991) proposes the exponential GARCH (EGARCH) model. In particular,
to allow for asymmetric effects between positive and negative asset returns,
he considers a weighted innovation function for the conditional variance. \

Basing ourselves in the AIC criterion, Ljung-Box test for residual autocorrelations and significance of the parameters we estimate an EGARCH-M(1,1), which takes into account the past 2 effects. 

\begin{align}
    r_t = \mu + \gamma\sigma^2_t + \epsilon_t,\hspace{0.5pt}\epsilon_t | \Omega_{t-1} \approx N(0,\sigma^2_t)\\
   \ln \sigma^2_t = \omega+\alpha(\dfrac{\epsilon_{t-1}}{\sigma_{t-1}}) + \gamma \|\dfrac{\epsilon_{t-1}}{\sigma_{t-1}}\| + \beta\ln\sigma^2_{t-1} +\delta\phi_t
\end{align}

where $r_t$ is the stock return at interval $t$, $\mu$ and $\omega$ are constant terms, $\epsilon_t$ are the serially uncorrelated errors of stock returns with mean zero,  $\sigma^2_t$
is the conditional variance of $\epsilon_t$,
whereas $\phi_t$ is market related information demand .\

In this framework we can interpret:\

- $\beta$ can be interpreted as the persistence of the model. \

- $\alpha$ relates standardized shocks to volatility in an
asymmetric style. For $\alpha$ < 0 the future conditional variances will increase
proportionally more as a result of a negative shock than for a positive shock
of the same absolute magnitude (Bollerslev, Mikkelsen, 1996).\

- $\gamma$ relates lagged standardized innovations
to volatility in a symmetric way.\

- $\delta$ represents the effect that market information demand has on conditional variance (at time $t$).\

- $\gamma$ represents the risk premium,
i.e., the increase in the expected rate of return due to an increase in the variance of the
return.\



```{r}

try_garch = function(model, vt, includemean, archm, go){
  
  
  id_ticker = unique(df$Ticker)

exo_levels = c('SPY')
exo_vol = c('market_info')
  GARCH_model <- function(x){
                      # ''' For ticker x estimate the GARCH model'''
                      x = x %>% 
                        arrange(Date)
                      # x =tail(x,200)
                      # Specify model
                      spec1 =ugarchspec(variance.model=list(model=model,variance.targeting =vt,
                                                            garchOrder = go,
                                  external.regressors =  as.matrix(subset(x, select = exo_vol))),
                  mean.model=list(armaOrder=c(0,0), include.mean=includemean, archm = archm),
distribution.model = 'sstd'
)
                      
                      # Fit model
                      fit = ugarchfit(spec = spec1, x$ret, solver = 'hybrid')
                      # Pvalues
                      Pvalues = fit@fit$robust.matcoef[,4]
                      names(Pvalues) =lapply(names(fit@fit$coef), function(x){return(paste0('p_',x))})
                      # Coeficients
                      Coeficients = fit@fit$robust.matcoef[,1]
                      
                      ret = c(Pvalues, Coeficients)
                      return(ret)
}

garch_results = df %>% 
  split(.$Ticker) %>% 
  map(GARCH_model)

garch_results = t(as.data.frame(garch_results))


print(sum(as.data.frame(garch_results)$p_vxreg1 < 0.1))
print(sum(as.data.frame(garch_results)$p_vxreg1 < 0.05))

return(garch_results)

}


garch_results = try_garch(model = 'eGARCH', vt = FALSE, includemean = TRUE, archm = TRUE, go = c(1,1))

colnames(garch_results)

```


Finally, write results to a csv file

```{r}
write.csv(garch_results, file = "/project/data/GARCH_results.csv")
```
